%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.4in}
\addtolength{\topmargin}{-.25in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Luke Pitstick} \\ \vspace{1pt}
    \small 512-701-4145 $|$ \href{mailto:luke.pitstick@colorado.edu}{\underline{luke.pitstick@colorado.edu}} $|$
    \href{https://lukepitstick.com}{\underline{lukepitstick.com}} $|$
    \href{https://www.linkedin.com/in/luke-pitstick/}{\underline{LinkedIn}} $|$
    \href{https://github.com/luke-pitstick}{\underline{GitHub}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Colorado Boulder}{Aug. 2024 -- May 2028}
      {Bachelor of Arts in Computer Science and Political Science}{Boulder, CO}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI/ML Engineer Intern}{Jun. 2026 -- Present}
      {WattByte Nexus}{Golden, CO}
      \resumeItemListStart
        \resumeItem{Design and implement physics-informed neural networks with PyTorch to predict and reduce wildfire risk from power-grid infrastructure.}
        \resumeItem{Build event-driven wildfire-risk simulations using NOAA weather data, AWS, and Redis to model grid assets, environmental conditions, and failure scenarios.}
        \resumeItem{Design and build an AWS pipeline using Fargate, SQS, and Glue to process video footage into segmented 3D representations.}
      \resumeItemListEnd

    \resumeSubheading
      {Junior Data Manager}{Oct. 2025 -- Present}
      {National Oceanic and Atmospheric Administration}{Boulder, CO}
      \resumeItemListStart
        \resumeItem{Automate ingestion, validation, and archival workflows for 10TB+/week of ocean acoustic data using Python, Oracle DB, and AWS S3.}
        \resumeItem{Maintain end-to-end sonar data workflows ingesting water column and passive acoustic data from NOAA research vessels into NCEI's national archive.}
        \resumeItem{Develop Python tools to automate QC and enforce metadata standards across oceanographic data submissions to NOAA/NCEI.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Science Intern}{Aug. 2025 -- Dec. 2025}
      {Ranked Choice Voting for Longmont}{Boulder, CO}
      \resumeItemListStart
        \resumeItem{Engineered high-resolution demographic maps in ArcGIS, R, and Python, enabling campaign teams to identify turnout gaps and execute targeted outreach.}
        \resumeItem{Developed fixed-effects regression models to predict voter turnout, allowing the campaign team to make targeted decisions.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------LEADERSHIP EXPERIENCE-----------
\section{Leadership Experience}
    \resumeSubHeadingListStart
    \resumeSubheading
      {Representative-at-Large \& Press Secretary}{May 2025 -- May 2026}
      {University of Colorado Student Government}{Boulder, CO}
      \resumeItemListStart
        \resumeItem{Supported allocation of a \$36M student budget across 12 cost centers, coordinating with university administrators to ensure equitable fund distribution.}
        \resumeItem{Led a 6-person team to increase student engagement across social media channels by 15\%.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Recipe Social Media App} $|$ \emph{React Native, Python, pgvector, Figma} $|$ \href{https://plateapp.framer.website/}{\underline{Launch Page}}}{June 2026 -- Present}
          \resumeItemListStart
            \resumeItem{Develop and design a social media recipe app that allows users to discover new recipes and plan their week.}
            \resumeItem{Build a personalized recipe recommendation engine using vector embeddings and pgvector to learn user preferences from swipe behavior.}
            \resumeItem{Develop a data pipeline in order to web scrape recipes, clean, and convert them to vector embeddings in order to deliver a wide variety of new content.}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{InfraDrone} $|$ \emph{Python, C++, PyTorch, TensorRT} $|$ \href{https://github.com/Luke-Pitstick/InfraDrone}{\underline{GitHub}}}{Apr. 2026 - Present}
          \resumeItemListStart
              \resumeItem{Design and build an autonomous drone and ground station using a Jetson Orin Nano, MAVLink, and TensorRT for offline road-damage surveys.}
            \resumeItem{Developed a custom AI pipeline to detect, classify, and calculate the severity of road damage using augmented YOLOv26 models resulting in 80\% precision and 75\% mAP@50.}
            \resumeItem{Implement a temporal engine to determine cracks growth over time using YOLO segmentation models and a custom GPS-based algorithm.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Renewably} $|$ \emph{Python, XGBoost, Polars, React, FastAPI} $|$ \href{https://renewably-wind.onrender.com/}{{\underline{Demo}}}}{Apr. 2026}
          \resumeItemListStart
            \resumeItem{Won 1st place at BlasterHacks 2026; built an interactive renewable energy siting platform with React and ArcGIS.}
            \resumeItem{Trained an XGBoost model on geospatial features to score wind-farm site viability against existing wind turbine locations. Achieved 96\% accuracy on validation data.}
            \resumeItem{Built a FastAPI optimization pipeline to evaluate thousands of candidate locations within user-defined regions.}
          \resumeItemListEnd
      
      
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, TypeScript, SQL, R} \\
     \textbf{Frameworks/Libraries}{: PyTorch, NumPy, scikit-Learn, pandas, Polars, ggplot2, Matplotlib, React, FastAPI} \\
     \textbf{Cloud/Databases}{: Redis, AWS, GCP, PostgreSQL,Modal, Render} \\
     \textbf{Other}{: Figma, ArcGIS, Bash, Linux, Git}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}